# (PART\*) Student Activity {-}

# Explore the Epigenome

## Launch the Genome Browser Gateway

Go to [`https://genome.ucsc.edu/cgi-bin/hgGateway`](https://genome.ucsc.edu/cgi-bin/hgGateway). Ensure "Human" is selected under "Browse/Select Species".  

```{r, fig.align='center', echo = FALSE, fig.alt= "Landing page for the UCSC Genome browser Gateway.", width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1B7y_jm8GuHZMUvTU1TFdW4nqQQV6nOT9XuFwgSflXz4/edit#slide=id.g15625333d53_0_2")
```

You will be working from the Human Assembly **March 2006 (NCBI/hg18)**. Make sure this is selected under the "Find Position" dropdown menu. Enter **HOXA7** in Position/Search Term and select GO. 

```{r, fig.align='center', echo = FALSE, fig.alt= "March 2006 assembly is highlighted on the Find Position dropdown menu."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1B7y_jm8GuHZMUvTU1TFdW4nqQQV6nOT9XuFwgSflXz4/edit#slide=id.g15625333d53_0_7")
```

Your Genome Browser should now look like this:

```{r, fig.align='center', echo = FALSE, fig.alt= "March 2006 assembly results for the HOXA7 locus."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1B7y_jm8GuHZMUvTU1TFdW4nqQQV6nOT9XuFwgSflXz4/edit#slide=id.g15625333d53_0_22")
```

## Clean up Visual Settings